Informing policy via dynamic models: Eliminating cholera in Haiti

### 2022-09-27 ms.Rnw
changed code to match updated haitipkg

  # Global search, All params
  SEARCH1 <- list(
    NP = 50, NMIF = 3, NREPS = 3,
    NREPS_EVAL = 3, NP_EVAL = 100
  )

  # Local search, unit specific params
  SEARCH2 <- list(
    TOP_N = 1, NP = 50, NMIF = 3, NREPS = 3, NREPS_EVAL = 3,
    NP_EVAL = 100
  )

  # Number of searches
  N_SEARCHES <- 2L

  # THESE SEARCHES AREN'T CONDUCTED
  SEARCH3 <- list(
    TOP_N = 1, NP = 20, NMIF = 3, NREPS = 3, NREPS_EVAL = 3, NP_EVAL = 25
  )

  SEARCH4 <- list(
    TOP_N = 1, NP = 20, NMIF = 3, NREPS = 3, NREPS_EVAL = 3, NP_EVAL = 25
  )

  SEARCH5 <- list(
    TOP_N = 1, NP = 20, NMIF = 3, NREPS = 3, NREPS_EVAL = 3, NP_EVAL = 25
  )
} else if (RUN_LEVEL == 2) {

@@

  # Local search, unit specific
  SEARCH2 <- list(
    TOP_N = 2, NP = 200, NMIF = 20, NREPS = 18, NREPS_EVAL = 36, NP_EVAL = 500
  )

  # Local search, shared parameters
  SEARCH3 <- list(
    TOP_N = 2, NP = 200, NMIF = 10, NREPS = 18, NREPS_EVAL = 36, NP_EVAL = 500
  )

  # Local search, unit specific
  SEARCH4 <- list(
    TOP_N = 2, NP = 200, NMIF = 10, NREPS = 18, NREPS_EVAL = 36, NP_EVAL = 500
  )

  # Local search, all parameters
  SEARCH5 <- list(
    TOP_N = 2, NP = 200, NMIF =  5, NREPS = 18, NREPS_EVAL = 36, NP_EVAL = 500
  )

  # Number of searches
  N_SEARCHES <- 5L
} else if (RUN_LEVEL == 3) {

  # Global search, all parameters
  SEARCH1 <- list(
    NP = 1500, NMIF = 100, NREPS = 144, NREPS_EVAL = 36, NP_EVAL = 2000
  )

  # Local search, unit specific parameters
  SEARCH2 <- list(
    TOP_N = 4, NP = 2000, NMIF = 100, NREPS = 18, NREPS_EVAL = 36, NP_EVAL = 4000
  )

  # Local search, shared parameters
  SEARCH3 <- list(
    TOP_N = 3, NP = 4000, NMIF = 50, NREPS = 24, NREPS_EVAL = 36, NP_EVAL = 5000
  )

  # Local search, unit specific parameters
  SEARCH4 <- list(
    TOP_N = 3, NP = 4000, NMIF = 50, NREPS = 24, NREPS_EVAL = 36, NP_EVAL = 5000
  )

  # Local search, all parameters
  SEARCH5 <- list(
    TOP_N = 3, NP = 4000, NMIF = 25, NREPS = 24, NREPS_EVAL = 36, NP_EVAL = 5000
  )

  # Total number of searches
  N_SEARCHES <- 5L
} else {
  stop("Run level must be 1, 2 or 3.")
}

if (RUN_LEVEL != 3 & file.exists("model3/run_level_3/haiti3_fit.rds")) {
  haiti3_fit <- readRDS("model3/run_level_3/haiti3_fit.rds")
} else {
  haiti3_fit <- bake(
    file = paste0("model3/", rl_dir, "haiti3_fit.rds"), {
      fit_haiti3(
        search1 = SEARCH1,
        search2 = SEARCH2,
        search3 = SEARCH3,
        search4 = SEARCH4,
        search5 = SEARCH5,
        n_searches = N_SEARCHES,
        ncores = cores
      )
    }
  )
}

rm(SEARCH1, SEARCH2, SEARCH3, SEARCH4, SEARCH5, N_SEARCHES)
gc()
@

@@

      # Get samples from filtering distribution
      s0_pf <- pfilter(s0, save.state = TRUE, Np = h1_scen_NP)

      # project vacc scenario, with filtering dist, and model.
      h1_S0_sims <- project_from_filter2(mod = s0, PF = s0_pf, nsims = h1_scen_sims)

@@

      # Get samples from filtering distribution for Scenario 2 model:
      s2_pf <- pfilter(s2, save.state = TRUE, Np = h1_scen_NP)

      # project vacc scenario, with filtering dist, and model.
      h1_S2_sims <- project_from_filter2(mod = s2, PF = s2_pf, nsims = h1_scen_NP)

@@

      # Get samples from filtering distribution for Scenario 2 model:
      s4_pf <- pfilter(s4, save.state = TRUE, Np = h1_scen_NP)

      # project vacc scenario, with filtering dist, and model.
      h1_S4_sims <- project_from_filter2(mod = s4, PF = s4_pf, nsims = h1_scen_NP)

@@

      # Get samples from filtering distribution for Scenario 2 model:
      s3_pf <- pfilter(s3, save.state = TRUE, Np = h1_scen_NP)

      # project vacc scenario, with filtering dist, and model.
      h1_S3_sims <- project_from_filter2(mod = s3, PF = s3_pf, nsims = h1_scen_NP)

@@

      # Get samples from filtering distribution for Scenario 2 model:
      s1_pf <- pfilter(s1, save.state = TRUE, Np = h1_scen_NP)

      # project vacc scenario, with filtering dist, and model.
      h1_S1_sims <- project_from_filter2(mod = s1, PF = s1_pf, nsims = h1_scen_NP)

@@

if (RUN_LEVEL != 3 & file.exists("model3/run_level_3/h3_bpf.rds")) {
  h3_bpf <- readRDS("model3/run_level_3/h3_bpf.rds")
} else {
  h3_bpf <- bake(
    file = paste0("model3/", rl_dir, "h3_bpf.rds"),
    expr = {
      bpfilter(h3Spat, Np = NP_BPF, block_size = 1, save_states = TRUE)
    },
    timing = FALSE
  )
}

@@

      # Using parameters and filtered distribution, project system
      h3_V0_sims <- project_from_filter2(
        h3Spat, PF = h3_bpf, covarGen = project_rain,
        nsims = NSIM, seed = 6897154
      )

@@

      # Using parameters and filtered distribution, project system
      h3_V1_sims <- project_from_filter2(
        h3Spat, PF = h3_bpf, covarGen = project_rain,
        nsims = NSIM, seed = 6897154
      )

@@

      # Using parameters and filtered distribution, project system
      h3_V2_sims <- project_from_filter2(
        h3Spat, PF = h3_bpf, covarGen = project_rain,
        nsims = NSIM, seed = 6897154
      )

@@

      # Using parameters and filtered distribution, project system
      h3_V3_sims <- project_from_filter2(
        h3Spat, PF = h3_bpf, covarGen = project_rain,
        nsims = NSIM, seed = 6897154
      )

@@

      # Using parameters and filtered distribution, project system
      h3_V4_sims <- project_from_filter2(
        h3Spat, PF = h3_bpf, covarGen = project_rain,
        nsims = NSIM, seed = 6897154
      )

>>>>

  # Global search, All parameters
  SEARCH1 <- list(NP = 20, NMIF = 3, NREPS = 3, NREPS_EVAL = 3, NP_EVAL = 25)

  # Local search, all parameters
  SEARCH2 <- list(
    TOP_N = 1, NP = 20, NMIF = 3, NREPS = 3, NREPS_EVAL = 3, NP_EVAL = 25
  )

  # Local search, unit specific parameters
  SEARCH3 <- list(TOP_N = 1, NP = 20, NMIF = 3, NREPS = 3, NREPS_EVAL = 3, NP_EVAL = 25)

  # Number of searches
  N_SEARCHES <- 3L

} else if (RUN_LEVEL == 2) {

@@

  # Local search, all parameters
  SEARCH2 <- list(
    TOP_N = 2, NP = 200, NMIF = 20, NREPS = 18, NREPS_EVAL = 36, NP_EVAL = 500
  )

  # Local search, unit specific parameters
  SEARCH3 <- list(
    TOP_N = 2, NP = 200, NMIF = 10, NREPS = 18, NREPS_EVAL = 36, NP_EVAL = 500
  )

  # Number of searches
  N_SEARCHES <- 3L
} else if (RUN_LEVEL == 3) {

  # Global search, all parameters
  SEARCH1 <- list(
    NP = 1500, NMIF = 100, NREPS = 144, NREPS_EVAL = 36, NP_EVAL = 2000,
    RW_SD = rw.sd(
      betaB = 0.02,   # Unit Specific
      foi_add = 0.02, # Unit Specific
      mu_B = 0.02,
      thetaI = 0.02,
      XthetaA = 0.02,
      lambdaR = 0.02,
      r = 0.01,
      std_W = 0.02,
      epsilon = 0.02,
      k = 0.02,
      sigma = 0.02
    )
  )

  # Local search, all parameters
  SEARCH2 <- list(
    TOP_N = 12, NP = 2000, NMIF = 100, NREPS = 6, NREPS_EVAL = 36, NP_EVAL = 3000,
    RW_SD = rw.sd(
      betaB = 0.0075,   # Unit Specific
      foi_add = 0.0075, # Unit Specific
      mu_B = 0.0075,
      thetaI = 0.0075,
      XthetaA = 0.0075,
      lambdaR = 0.0075,
      r = 0.005,
      std_W = 0.0075,
      epsilon = 0.0075,
      k = 0.0075,
      sigma = 0.0075
    )
  )

  # Local search, unit specific parameters
  SEARCH3 <- list(
    TOP_N = 9, NP = 2000, NMIF = 100, NREPS = 8, NREPS_EVAL = 36, NP_EVAL = 4000,
    RW_SD = rw.sd(
      betaB = 0.005,
      foi_add = 0.005
    )
  )

  # Total number of searches
  N_SEARCHES <- 3L
} else {
  stop("Run level must be 1, 2 or 3.")
}

if (RUN_LEVEL != 3 & file.exists("model3/run_level_3/haiti3_fit.rds")) {
  haiti3_fit <- readRDS("model3/run_level_3/haiti3_fit.rds")
} else {
  haiti3_fit <- bake(
    file = paste0("model3/", rl_dir, "haiti3_fit.rds"), {
      fit_haiti3(
        search1 = SEARCH1,
        search2 = SEARCH2,
        search3 = SEARCH3,
        n_searches = N_SEARCHES,
        ncores = cores
      )
    }
  )
}

rm(SEARCH1, SEARCH2, SEARCH3, N_SEARCHES)
gc()
@

@@

      # Get samples from filtering distribution
      s0_pf <- pfilter(s0, save.state = TRUE, Np = h1_scen_NP)
      end_states <- saved.states(s0_pf)
      end_states <- end_states[[length(end_states)]]

      # project vacc scenario, with filtering dist, and model.
      h1_S0_sims <- project_from_filter(mod = s0, end_states = end_states, nsims = h1_scen_sims)

@@

      # Get samples from filtering distribution for Scenario 2 model:
      s2_pf <- pfilter(s2, save.state = TRUE, Np = h1_scen_NP)
      end_states <- saved.states(s2_pf)
      end_states <- end_states[[length(end_states)]]

      # project vacc scenario, with filtering dist, and model.
      h1_S2_sims <- project_from_filter(mod = s2, end_states = end_states, nsims = h1_scen_NP)

@@

      # Get samples from filtering distribution for Scenario 2 model:
      s4_pf <- pfilter(s4, save.state = TRUE, Np = h1_scen_NP)
      end_states <- saved.states(s4_pf)
      end_states <- end_states[[length(end_states)]]

      # project vacc scenario, with filtering dist, and model.
      h1_S4_sims <- project_from_filter(mod = s4, end_states = end_states, nsims = h1_scen_NP)

@@

      # Get samples from filtering distribution for Scenario 2 model:
      s3_pf <- pfilter(s3, save.state = TRUE, Np = h1_scen_NP)
      end_states <- saved.states(s3_pf)
      end_states <- end_states[[length(end_states)]]

      # project vacc scenario, with filtering dist, and model.
      h1_S3_sims <- project_from_filter(mod = s3, end_states = end_states, nsims = h1_scen_NP)

@@

      # Get samples from filtering distribution for Scenario 2 model:
      s1_pf <- pfilter(s1, save.state = TRUE, Np = h1_scen_NP)
      end_states <- saved.states(s1_pf)
      end_states <- end_states[[length(end_states)]]

      # project vacc scenario, with filtering dist, and model.
      h1_S1_sims <- project_from_filter(mod = s1, end_states = end_states, nsims = h1_scen_NP)

@@

if (RUN_LEVEL != 3 & file.exists("model3/run_level_3/h3_bpf_end_states.rds")) {
  h3_bpf_end_states <- readRDS("model3/run_level_3/h3_bpf_end_states.rds")
} else {
  h3_bpf_end_states <- bake(
    file = paste0("model3/", rl_dir, "h3_bpf_end_states.rds"),
    expr = {
      h3_bpf <- bpfilter(h3Spat, Np = NP_BPF, block_size = 1, save_states = TRUE)
      ss <- h3_bpf@saved.states
      ss[[length(ss)]]
    },
    timing = FALSE
  )
}

@@

      # Using parameters and filtered distribution, project system
      h3_V0_sims <- project_from_filter(
        h3Spat, end_states = h3_bpf_end_states, covarGen = project_rain,
        nsims = NSIM, seed = 6897154
      )

@@

      # Using parameters and filtered distribution, project system
      h3_V1_sims <- project_from_filter(
        h3Spat, end_states = h3_bpf_end_states, covarGen = project_rain,
        nsims = NSIM, seed = 6897154
      )

@@

      # Using parameters and filtered distribution, project system
      h3_V2_sims <- project_from_filter(
        h3Spat, end_states = h3_bpf_end_states, covarGen = project_rain,
        nsims = NSIM, seed = 6897154
      )

@@

      # Using parameters and filtered distribution, project system
      h3_V3_sims <- project_from_filter(
        h3Spat, end_states = h3_bpf_end_states, covarGen = project_rain,
        nsims = NSIM, seed = 6897154
      )

@@

      # Using parameters and filtered distribution, project system
      h3_V4_sims <- project_from_filter(
        h3Spat, end_states = h3_bpf_end_states, covarGen = project_rain,
        nsims = NSIM, seed = 6897154
      )
